Verifying Demonstrations

### 2018-05-24 paper/analysis-security.tex
Completes spatial eligibility, privacy left

\Cref{TemporallyRelated} ensures freshness, \ie that we cannot simply resubmit 
an old proof as a new one.
In general, freshness requires the prover to respond to an unpredictable 
challenge.
The challenge here is to include the hash value at the head of the blockchain at 
the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof 
share).
As per construction of blockchains, the hash value at the head depends on the 
previous blocks in the chain.
Thus the predictability of \(t_s\) depends on the predictability of the blocks, 
which depends on the predictability of the transactions and the nonce needed by 
the miner.
The transactions in turn depend on the signatures made by the signing keys 
corresponding to the used transactions.
If these were predictable, our adversary could spend arbitrary transactions in 
the blockchain --- which is designed to be hard.
Thus Alice can predict \(t_s\) with negligible probability, \ie \(t_s\) must 
have been published on the blockchain before being included in her proof share.

According to \cref{TemporallyRelated}, we must also prove that a proof share has 
not been created after a certain time.
The hash values of the proof shares are committed to the blockchain, thus there 
is a negligible probability that they were created after that.
Alice would have to choose a value \(y\) in the domain of the hash function 
\(\Hash\) and then find a preimage \(x\) such that \(y = \Hash[x]\) and \(x\) is 
a valid proof.
If \(\Hash\) is collision resistant, then finding \emph{any} preimage is hard.

@@

\daniel{Discuss the two alternative approaches: trusted Jane and collusion 
  threshold.
  Do actual security analysis.}
According to \cref{SpatiallyRelated} Alice and Bob must bind their proofs 
(shares) spatially to the location, which would allow us to verify that they 
were actually in that location.
The role of the witnesses is to provide this property.

@@

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
\(\sk_P'\) and make the witness accept in the protocol
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid], \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
This is thus reduced to the security of the \(\AC\) scheme and how often Alice 
can get a valid signature on a secret key from the \ac{CA}.

@@

\paragraph{Forging proof shares}

\daniel{This is work-in-progress.}
Alice can attempt to forge the full proof directly, \ie
\begin{multline*}
\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
  \begin{aligned}
    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
  \end{aligned} \\
    (\cid, \pid', \wid', t_s, t_s', l, \wsig')
\end{multline*}
and consequently
\begin{multline*}
  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid'] \quad \land \\
      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid', \wid', t_s, t_s', l, \wsig'),
\end{multline*}
and thus solve same problem twice (once for \(pid'\) and once for \(\wid'\)).

>>>>

\Cref{TemporallyRelated} ensures freshness, \ie that Alice cannot simply 
resubmit an old proof as a new one.
In general, freshness requires the prover to respond to an unpredictable 
challenge.
The challenge here is to include the hash value at the head of the blockchain at 
the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof 
share).
As per construction of blockchains, the hash value at the head depends on the 
previous blocks in the chain.
Thus the predictability of \(t_s\) depends on the predictability of the blocks, 
which depends on the predictability of the transactions and the nonce needed by 
the miner.
The transactions in turn depend on the signatures made by the signing keys 
corresponding to the used transactions.
If these were predictable, our adversary could spend arbitrary transactions in 
the blockchain --- which is designed to be hard.
Thus Alice can predict \(t_s\) with negligible probability, \ie \(t_s\) must 
have been published on the blockchain before being included in her proof share.

According to \cref{TemporallyRelated}, we must also prove that a proof share has 
not been created after a certain time.
Otherwise Grace can argue that the proof share was created after the protest.
The hash values of the proof shares are committed to the blockchain, thus there 
is a negligible probability that they were created after that.
Alice would have to choose a value \(y\) in the domain of the hash function 
\(\Hash\) and then find a preimage \(x\) such that \(y = \Hash[x]\) and \(x\) is 
a valid proof.
If \(\Hash\) is collision resistant, then finding \emph{any} preimage is hard.

@@

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed on the location when the proof share was created.
Thus we must ensure that Alice cannot forge undeserved witness signatures.
To forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l, \wsig'),
\end{multline*}
while not knowing a signature on the secret key \(\sk_W'\).
Thus she must get break the \(\AC\) scheme to succeed or get a valid signature 
on \(\sk_W'\) from the \ac{CA}.

@@

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that Alice can 
provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
\(\sk_P'\) and make the witness accept in the protocol
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
This is thus reduced to the security of the \(\AC\) scheme and how often Alice 
can get a valid signature on a secret key from the \ac{CA}.

@@

%\paragraph{Forging proof shares}
%
%\daniel{This is work-in-progress.}
%Alice can attempt to forge the full proof directly, \ie
%\begin{multline*}
%\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
%  \begin{aligned}
%    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
%    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
%  \end{aligned} \\
%    (\cid, \pid', \wid', t_s, t_s', l, \wsig')
%\end{multline*}
%and consequently
%and thus solve same problem twice (once for \(pid'\) and once for \(\wid'\)).
%

\subsection{Privacy}

\daniel{Must write up privacy analysis.
  However, must complement the privacy definition for this.}
